Lapse & Vision Loss PS Analysis

### 2025-02-24 analysis.Rmd
wip

    if (file.exists(filename) && !rerun_model) {
      print("Results are cached. Proceeding to next method...")
      method_results <- readRDS(filename)

      if (file.exists(diagnostics_filename) && !rerun_diagnostics) {
        diagnostics <- readRDS(diagnostics_filename)
        method_results <- c(method_results, diagnostics)
      }

      all_results[[params$name]] <- method_results
      next
    }

    print("No cached results found. Running method...")

@@

@@

    if (rerun_diagnostics) {
      balance_plot <- tryCatch({
        love.plot(result, stat = "mean.diffs", var.order = "adjusted", stars = "std")
      }, error = function(e) {
        message("Error generating balance plot for ", params$name, ": ", e)
        return(NULL)
      })

      if (!params$method %in% c("nearest_mahalanobis", "cem")) {
        common_support_plot <- tryCatch({
          if (params$method == "twang") {
            bal.plot(result, var.name = "prop.score.es.mean", which = "both")
          } else {
            bal.plot(result, var.name = "distance", which = "both")
          }
        }, error = function(e) {
          message("Error generating common support plot for ", params$name, ": ", e)
          return(NULL)
        })
      }

      balance_summary <- tryCatch({
        if (params$method == "twang") {
          summary(result)
        } else {
          bal.tab(result)
        }
      }, error = function(e) {
        message("Error generating balance summary for ", params$name, ": ", e)
        return(NULL)
      })
    }

    method_results <- list(result = result)
    saveRDS(method_results, file = filename)

    diagnostics <- list(balance_plot = balance_plot, common_support_plot = common_support_plot, summary = balance_summary)
    saveRDS(diagnostics, file = diagnostics_filename)

    all_results[[params$name]] <- c(method_results, diagnostics)
  }

>>>>

    result <- NULL

    if (file.exists(filename) && !rerun_model) {
      print("Loading cached results...")
      result <- readRDS(filename)$result
    }

    if (is.null(result)) {
      print("No cached results found or rerunning model. Running method...")

@@

      if (!is.null(result)) {
        saveRDS(list(result = result), file = filename)
      }
    }

@@

    if (rerun_diagnostics || !file.exists(diagnostics_filename)) {
      print("Running diagnostics...")

      balance_plot <- tryCatch({
        love.plot(result, stat = "mean.diffs", var.order = "adjusted", stars = "std")
      }, error = function(e) {
        message("Error generating balance plot for ", params$name, ": ", e)
        return(NULL)
      })

      common_support_plot <- tryCatch({
        if (params$method == "twang") {
          bal.plot(result, var.name = "prop.score.es.mean", which = "both")
        } else {
          bal.plot(result, var.name = "distance", which = "both")
        }
      }, error = function(e) {
        message("Error generating common support plot for ", params$name, ": ", e)
        return(NULL)
      })

      balance_summary <- tryCatch({
        if (params$method == "twang") {
          summary(result)
        } else {
          bal.tab(result)
        }
      }, error = function(e) {
        message("Error generating balance summary for ", params$name, ": ", e)
        return(NULL)
      })

      saveRDS(list(balance_plot = balance_plot, common_support_plot = common_support_plot, summary = balance_summary), file = diagnostics_filename)
    } else {
      print("Loading cached diagnostics...")
      diagnostics <- readRDS(diagnostics_filename)
      balance_plot <- diagnostics$balance_plot
      common_support_plot <- diagnostics$common_support_plot
      balance_summary <- diagnostics$summary
    }

    all_results[[params$name]] <- list(
      result = result,
      balance_plot = balance_plot,
      common_support_plot = common_support_plot,
      summary = balance_summary
    )
  }
